Meta-analysis

### 2019-08-06 03_Preliminary_analysis.Rmd
Added investigation into the role of fungicide on proportion of yield gain

#### Effect of Fungicide 
**on proportional yield gain with repect to time of application**
First lets look at the quantiles for each fungicide irrespective of other factors.
We will focus on proportional yield gain, compared to no treatment control, as this should partially correct for some spatial and seasonal effects.  
```{r}
PM_MB_means %>%
   group_by(Fungicide) %>%
   summarise(n = length(prop_YG),
             lower_2.5 = quantile(prop_YG, na.rm = T, c(0.025)),
             median = median(prop_YG, na.rm = T),
             mean = mean(prop_YG, na.rm = T),
             upper_97.5 = quantile(prop_YG, na.rm = T, c(0.975))) %>%
   filter(n >= 5) %>% # remove any fungicide groups with less than 5 observations
   arrange(desc(median)) %>%
   kable(caption = "Fungicide effect on proportion of yield gain") %>%
   kable_styling(fixed_thead = T, full_width = T)

# plot table as a density plot

ggplot(PM_MB_means, aes(prop_YG))+
   geom_density(aes(fill = cut(PM_MB_means2$spray_diff, c(-30,-19,-15,-10,-1,2,7,10,12,21))), alpha = 0.5)+
   geom_vline(aes(xintercept = 0), size =0.5)+
   facet_grid(cut(PM_MB_means2$spray_diff, c(-30,-19,-15,-10,-1,2,7,10,12,21))~.)+
   #scale_fill_discrete(labels = c("15-7 days before","same day","one day after","8-9 days after","13-19 days after"))+
   labs(x = "Proportion of grain yeild saved",
   title = "Grain yield proportion saved grouped by\nwhen the first Sulphur fungicide application was made\nrelative to when Powdery Mildew was first seen")+
   theme(panel.grid.major = element_line(colour = "grey80"),
         panel.grid.minor = element_line(colour = "grey50"),
         panel.background = element_rect(fill = NA))+
   guides(fill=guide_legend(title="Days (binned)\nfirst spray \nwas applied\nrelative to\nFirst sign of disease"))+
   scale_x_continuous(limits = c(-0.3,0.6))

>>>>

#### Effect of Fungicide 
**on proportional yield gain with repect to time of application**
First lets look at the quantiles for each fungicide irrespective of other factors.
We will focus on proportional yield gain, compared to no treatment control, as this should partially correct for some spatial and seasonal effects.  
```{r fungicide_proportion_yield}
PM_MB_means %>%
   group_by(Fungicide) %>%
   summarise(n = length(prop_YG),
             lower_2.5 = quantile(prop_YG, na.rm = T, c(0.025)),
             median = median(prop_YG, na.rm = T),
             mean = mean(prop_YG, na.rm = T),
             upper_97.5 = quantile(prop_YG, na.rm = T, c(0.975))) %>%
   filter(n >= 5) %>% # remove any fungicide groups with less than 5 observations
   arrange(desc(median)) %>%
   kable(caption = "Fungicide effect on proportion of yield gain") %>%
   kable_styling(fixed_thead = T, full_width = T)

# plot table as a box plot

ggplot(PM_MB_means, aes(y = prop_YG, x = Fungicide))+
   geom_boxplot()+
   geom_hline(aes(yintercept = 0), size =0.5)+
   #scale_fill_discrete(labels = c("15-7 days before","same day","one day after","8-9 days after","13-19 days after"))+
   labs(x = "Proportion of grain yeild saved",
   title = "Grain yield proportion saved grouped by\nFungicide type")+
   theme(panel.grid.major = element_line(colour = "grey80"),
         panel.grid.minor = element_line(colour = "grey50"),
         panel.background = element_rect(fill = NA))+
   guides(fill=guide_legend(title="Fungicide"))+
   coord_cartesian()+
   theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.3))
   #scale_x_continuous(limits = c(-0.3,0.6))

```
There was some hope groups of fungicide could be combined, ie Propiconazole and Tebeconazole, however it seems that they have different efficacies. Let us look to see if there is anything skewing the above.

```{r Fungicide_x_nSprays}
PM_MB_means %>%
   group_by(Fungicide, total_Fungicide) %>%
   summarise(n = length(prop_YG),
             lower_2.5 = quantile(prop_YG, na.rm = T, c(0.025)),
             median = median(prop_YG, na.rm = T),
             mean = mean(prop_YG, na.rm = T),
             upper_97.5 = quantile(prop_YG, na.rm = T, c(0.975))) %>%
   filter(n >= 5) %>% # remove any fungicide groups with less than 5 observations
   arrange(desc(median)) %>%
   kable(caption = "Fungicide effect on proportion of yield gain") %>%
   kable_styling(fixed_thead = T, full_width = T)

PM_MB_means %>%
   filter(total_Fungicide ==1 |total_Fungicide ==2 ) %>%
ggplot(aes(y = prop_YG, x = Fungicide))+
   facet_grid(cols = vars(total_Fungicide))+
   geom_boxplot(aes(fill = Fungicide, alpha = 0.5))+
   geom_hline(aes(yintercept = 0), size =0.5)+
   #scale_fill_discrete(labels = c("15-7 days before","same day","one day after","8-9 days after","13-19 days after"))+
   labs(x = "Proportion of grain yeild saved",
   title = "Grain yield proportion saved grouped by\nFungicide type")+
   theme(panel.grid.major = element_line(colour = "grey80"),
         panel.grid.minor = element_line(colour = "grey50"),
         panel.background = element_rect(fill = NA))+
   guides(fill=guide_legend(title="Fungicide"))+
   coord_cartesian()+
   theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.3))
   #scale_x_continuous(limits = c(-0.3,0.6))

Lets run this by a quick linear mixed effect model
```{r Fungicide_lmer}
levels(PM_MB_means$Fungicide)

PM_MB_means$Fungicide <- factor(PM_MB_means$Fungicide, levels = c("control","propiconazole","Tebeconazole",
                                                        "Amistar",
                                                        "200 g/l  Tebuconazole + 120 g/l  Azoxystrobin", "Carbendazim",
                                                        "Benomyl",  
                                                         "Pyrazophos","Acibenzolar-S-Methyl",
                                                        "Sulphur", "Sulphur (SC)","Sulphur (Ultra SC)","Sulphur (WP)"
                                                        ))

PM_MB_lmer.1 <- lmer(prop_YG ~ Fungicide + as.factor(total_Fungicide) + row_spacing + (1|Trial_ref), 
     data = subset(PM_MB_means, total_Fungicide == 1 | total_Fungicide == 2))

summary(PM_MB_lmer.1)

```
There is no significant difference between Fungicides, except for Sulphur which is significantly less effective than propiconazole. Propiconazole, on average, out performs other fungicides when mitigating yield loss.

How many trials contain all of the most studied fungicides
```{r}
Tebe_trials <- unique(PM_MB_means[PM_MB_means$Fungicide == "Tebeconazole",]$Trial_ref)
Propi_trials <- unique(PM_MB_means[PM_MB_means$Fungicide == "propiconazole",]$Trial_ref)
Amistar_trials <- unique(PM_MB_means[PM_MB_means$Fungicide == "Amistar",]$Trial_ref)

intersect(
   intersect(Tebe_trials,Propi_trials)
   ,Amistar_trials)
